---
title: "Twitter Celebrities Tweets Task"
autor: "Tal Waitzenberg and Lital Moali"
date: "June 18, 2017"
---
#The Task
We have chosen the third task
**Our Goal:** : Modeling Twitter celebrity tweets and creating new tweets by using this model.
#Data collection:
We have collected data from twitter using twitter search's API. 
The data we have collected was 179 tweets for 5 particular celebrities, we were using access tokens that allows collecting this data by permissions.

##c. Data collection documentation:    
c.1) Install and Activate Packages
```{r}
folder = 'C:/Users/talon/Desktop/shitot/FinalProject'
setwd(folder)
#install.packages("twitteR")
#install.packages("RJSONIO")
#install.packages("RCurl")
#install.packages("stringr")
library(twitteR)
library(RCurl)
library(RJSONIO)
library(stringr)
```

c.2) Declare Twitter API Credentials
```{r}
api_key <- "API KEY" # From dev.twitter.com
api_secret <- "API Secret" # From dev.twitter.com
token <- "Access token" # From dev.twitter.com
token_secret <- "Access token secret" # From dev.twitter.com
```

```{r}
api_key <- "IaBTQDeaXUeoeZJyP7IJcNmad"
api_secret <- "fYtrsLGr62x1JREaHrTZUOdmB2unNNVAM6KqY4aivOR8VMN7EG"
token <- "876433937958133760-bdNHlxWk1DSwcDlUyTbkLBatGrdSITv"
token_secret <- "wKaMWm0K5cybr3vtN0rgbWgNQtPUhdAg4YCYY6ERN7ov0"
```

c.3) Create Twitter Connection
```{r}
setup_twitter_oauth(api_key, api_secret, token, token_secret)
```

c.4) Run Twitter Search for the celebrities: Donald J. Trump, Kim Kardashian West, Kent Beck, Bill Gates, Katy Perry
```{r}
TrumpTweets <- searchTwitter("from:realDonaldTrump", n=50, lang="en")
KimKardashianTweets <- searchTwitter("from:KimKardashian", n=50, lang="en")
KentBecktweets <- searchTwitter("from:KentBeck", n=50, lang="en")
BillGatesTweets <- searchTwitter("from:BillGates", n=50, lang="en")
katyperryTweets <- searchTwitter("from:katyperry", n=50, lang="en")
allTweets <- c(TrumpTweets, KimKardashianTweets, KentBecktweets, BillGatesTweets, katyperryTweets)
allTweets.df <- twListToDF(allTweets)
```

c.5) Write the tweets to csv file
```{r}
write.csv(allTweets.df, file = "AllTweets.csv")
```

c.6) Read celebrities tweets from the csv file:
```{r}
tweets <- read.csv('AllTweets.csv', header = T)
tweets
```

c.7) Analizing the data
A quick summary of the new calculated features:
```{r}
summary(tweets)
```
Therefore we have chosen the following features:
```{r}
tweetsFeatures.df <- allTweets.df[c('text', 'favoriteCount', 'created', 'replyToSN', 'replyToSID', 'id', 'replyToUID', 'screenName', 'retweetCount')]
```

##Feature Engineering
Now we will add some calculated features
```{r}
#Number of characters per tweet
tweetsFeatures.df$text_length<- apply(tweetsFeatures.df, 1, function(x) nchar(x['text']))
#Number of words per tweet
nword <- function(str) { sapply(gregexpr("\\W+", str), length) + 1 }  
tweetsFeatures.df$number_of_word <- apply(tweetsFeatures.df, 1, function(x) nword(x['text']))
```

A quick summary of the new calculated features:
```{r}
summary(tweetsFeatures.df[,c('text_length','number_of_word')])

```

Visualize numeric features:

```{r}
trump <- subset(tweetsFeatures.df,screenName=='realDonaldTrump')
KimKardashian <- subset(tweetsFeatures.df,screenName=='KimKardashian')
KentBeck <- subset(tweetsFeatures.df,screenName=='KentBeck')
BillGates <- subset(tweetsFeatures.df,screenName=='BillGates')
katyperry <- subset(tweetsFeatures.df,screenName=='katyperry')


hist(trump$number_of_word,col='green',breaks=30,main='Donald Trump',xlab ='number of words' )
abline(v=median(trump$number_of_word),lwd=4)

hist(KimKardashian$number_of_word,col='red',breaks=30,main='Kim Kardashian',xlab ='number of words' )
abline(v=median(KimKardashian$number_of_word),lwd=4)

hist(KentBeck$number_of_word,col='blue',breaks=30,main='Kent Beck',xlab ='number of words' )
abline(v=median(KentBeck$number_of_word),lwd=4)

hist(BillGates$number_of_word,col='yellow',breaks=30,main='Bill Gates',xlab ='number of words' )
abline(v=median(BillGates$number_of_word),lwd=4)

hist(katyperry$number_of_word,col='orange',breaks=30,main='Katy Perry',xlab ='number of words' )
abline(v=median(katyperry$number_of_word),lwd=4)
```

